TESTI!!!

# Insert chapter 2 title here

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using  

```{r data, echo=FALSE, include=FALSE}

lrn14<- read.table("data/analysis_lrn2014_teksti.txt")

```
```{r}
str(lrn14)
dim(lrn14)

summary(lrn14)
```

```{r dims, echo=FALSE}
dim(lrn14)
str(lrn14)
```


```{r warning=FALSE}
library(ggplot2)
library(GGally)
```

```{r}
summary(lm(Points~Attitude,data=lrn14))

hei<-lm(Points~ Attitude, data=lrn14)

plot(hei)



```

```{r}
qplot(Attitude, Points, data = lrn14) + geom_smooth(method = "lm")



my_model <- lm(Points ~ Age+ Attitude+stra, data = lrn14)
summary(my_model)
```

# Jos vain 1 selittävä, intercept: mikäli attitude 0, niin pisteitä 11.
# multiple r-squared: korkerroin

```{r}
ggpairs(lrn14, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
```

```{r}
plot(lm(Points~Attitude, data=lrn14), which = c(1,2,5), par(mfrow=c(2,2)) )
```

```{r}
plot(lm(Points~Attitude, data=lrn14), which = c(1,2,5), par(mfrow=c(2,2)) )
```
